running pipeline

### 2023-07-06 scripts/running_pipeline.Rmd
Barneby hath risen and full pipe run complete

```{r setup, message=F}
library(tidyverse)
library(BarnebyLives)
```

@@

```{r load through google sheets, eF}

@@

names <- sf::st_drop_geometry(data) |>
  pull(Full_name)

names_vec <- c('Astragalis purshii', 'Linnaea borealius var. borealis', 'Heliumorus multifora')

lapply(FUN = spell_check, X = names_vec, path = '/hdd/Barneby_Lives-dev/taxonomic_data')

@@

POW_names <- lapply(data$Full_name, powo_searcher) |>
  bind_rows()
```

@@

directions2site <- directions_grabber(data, api_key = SoS_gkey)
```

@@

# we will add these data onto our final sheet.  THIS IS THE LAST STEP OF THIS TUTORIAL
sheet_append('1iOQBNeGqRJ3yhA-Sujas3xZ2Aw5rFkktUKv3N_e4o8M', 
             sheet = 'Processed - Examples', data = df)

>>>>

```{r setup, message = F}
library(tidyverse)
library(BarnebyLives)
```

@@

```{r load through google sheets}

@@

names <- data$Full_name
spellchecks <- lapply(FUN = spell_check, X = names, path = '/hdd/Barneby_Lives-dev/taxonomic_data') |>
  bind_rows() %>% 
  filter(Match == 'fuzzy')

head(spellchecks)

rm(names)
```

@@

POW_names <- lapply(data$Full_name, powo_searcher) |>
  bind_rows()

data <- bind_cols(data, POW_names) %>% 
  relocate(starts_with('POW_'), .before = geometry)

dplyr::select(data, starts_with('POW')) |>
  sf::st_drop_geometry() |>
  utils::head()
```

@@

directions2site <- directions_grabber(data, api_key = SoS_gkey)

@@

# we will add these data onto our final sheet.  THIS IS THE LAST STEP OF THIS TUTORIAL
googledata <- sf::st_drop_geometry(directions2site) %>% 
  dplyr::select(-UNIQUEID)

write_sheet( ss = '1iOQBNeGqRJ3yhA-Sujas3xZ2Aw5rFkktUKv3N_e4o8M', 
             sheet = 'Processed - Examples', data = googledata)

?gs4_create
```
